---
title: "08-plot"
author: "Pablo Haya"
date: "9/6/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Leemos datos

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(here)
load(here("data","core_dataset_clean.RData"))
```

## Histogramas

```{r echo TRUE}
summary(df$PayRate)
```

---

```{r echo=TRUE}
hist(df$PayRate)
```

---

```{r}
hist(df$PayRate, breaks = 5)
```

```{r}
hist(df$PayRate, breaks = 30)
```

---

```{r}
hist(df$PayRate, 
     main="Esto es el título", sub="Esto es un subtítulo",
     xlab="PayRate", ylab="Count")
```

## plot

```{r}
plot(df$DOB, df$PayRate)
```

---

```{r}
plot(df$DOB, df$PayRate,
     main="Title", sub="subtitle",
     xlab="Año", ylab="PayRate")
```

---

```{r}
plot(df$DOB, df$PayRate, col=df$Sex,
     main="Title", sub="subtitle",
     xlab="Año", ylab="PayRate")
```

---

```{r}
plot(df$DOB, df$PayRate, col=df$Sex,
     main="Title", sub="subtitle",
     xlab="Año", ylab="PayRate")
# No se que pasa con la leyenda
#legend(7, 4.3, levels(df$Sex), col=1:length(df$Sex), pch=1)
```


---

```{r echo=FALSE}
#++++++++++++++++++++++++++++++++++++++++++++
#generate a plot of point shapes which R knows about.
#++++++++++++++++++++++++++++++++++++++++++++
# source: http://www.sthda.com/english/wiki/r-plot-pch-symbols-the-different-point-shapes-available-in-r
generateRPointShapes<-function(){
  oldPar<-par()
  par(font=2, mar=c(0.5,0,0,0))
  y=rev(c(rep(1,6),rep(2,5), rep(3,5), rep(4,5), rep(5,5)))
  x=c(rep(1:5,5),6)
  plot(x, y, pch = 0:25, cex=1.5, ylim=c(1,5.5), xlim=c(1,6.5), 
       axes=FALSE, xlab="", ylab="", bg="blue")
  text(x, y, labels=0:25, pos=3)
  par(mar=oldPar$mar,font=oldPar$font )
}
generateRPointShapes()
```

## Series temporales

Pintar la evoluación en la contratación

```{r}

```


## Gráfico de barras

```{r}
count <- table(df$Department)
barplot(count, col="white",
        main="Title", sub="subtitle",
        xlab="Departamento", ylab="Número empleados")
```

---

```{r}
count <- table(df$Sex, df$Department)
barplot(count, 
        main="Title", sub="subtitle",
        xlab="Departamento", ylab="Número empleados",
        col=c("red", "darkblue"), legend = rownames(count))
```

---

```{r}
count <- table(df$Sex, df$Department)
barplot(count, 
        main="Title", sub="subtitle",
        xlab="Departamento", ylab="Número empleados",
        col=c("red", "darkblue"), legend=rownames(count), beside=TRUE)
```

---

```{r}
count <- table(df$Sex, df$Department)
barplot(count, 
        main="Title", sub="subtitle",
        xlab="Departamento", ylab="Número empleados",
        col=c("red", "darkblue"), legend=rownames(count), 
        beside=TRUE, horiz=TRUE)
```

## Boxplots

```{r}
plot(df$Sex, df$PayRate, main="Title", sub="subtitle",
  xlab="Sex", ylab="PayRate")
# que pasa con la leyenda
legend(7, 4.3, levels(df$Sex), pch=1)
```

---
Visualizar: plot, line, par, pairs
Line plots


When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

